The following are the initial codes given. It mainly purposed to clear existing objects,and create individual data.

```{r}
rm(list = ls())
options(warn=-1)
# The following are existing info
student_id <- 33521352
focus_country = "AND"
focus_country_full = "Andorra"

# Library needed
library(reshape2) 
library(ggplot2) 
library(dplyr)
library(tidyr)
library(corrplot)
```

```{r}
set.seed(student_id)  
VCData = read.csv("WVSExtract.csv") 
VC = VCData[sample(1:nrow(VCData),50000, replace=FALSE),] 
VC = VC[,c(1:6, sort(sample(7:46,17, replace = FALSE)), 47:53, 
sort(sample(54:69,10, replace = FALSE)))] 
```

Initial overview of code is as follows:

```{r}
head(VC)
```

**Data preprocessing**

In overall, there are `r nrow(VC)` rows and `r ncol(VC)` columns.

Although the data are coded in numerical scale, negative values which indicate missing values are still required to be treated. They will be replaced by `NA`.

```{r}
VC[VC < 0] <- NA 
```

Only categorical nominal data are treated as categorical, while the rest are treated as numerical (including categorical ordinal data). Therefore:

```{r}
categorical_names <- c("EEquality","EPrivate","EGovernment","ECompetition","EHardWork","PIA","PIAB","PNewspaper","PTelevision","PRadio","PMobile","PEmail","PInternet","PSocial","PFriends", "Country", "MF") #Here is predefined cols, for all data available in assignment instruction. It may include cols that doesnt exist.
numerical_names <- setdiff(names(VC), categorical_names)

numerical <- VC[, !names(VC) %in% categorical_names]

categorical <- VC[, names(VC) %in% categorical_names]
```

**Question 1**

Dimensions of data (col × row)

```{r}
dim(VC)
```

Check data types

```{r}
sapply(VC, class)
```

Checking there is any missing values

```{r}
na_counts <- colSums(is.na(VC))
na_counts
```

Checking the distribution of numerical variables

```{r}
head(numerical)
```

Distribution

```{r}
par(mar = c(2, 7, 2, 2))  
boxplot(numerical[, names(numerical) != "Age"],
        col = "lightblue", 
        horizontal = TRUE,  
        las = 2,
        main = "Distribution of Numeric Variables (Excluding Age)")

par(mar = c(7, 3, 2, 2))  
boxplot(numerical$Age, 
        main = "Distribution of Age Variable",
        col = "lightblue",
        las = 2,
        horizontal = TRUE)
```

Variety of non-numerical attributes (How many unique countries are there)

```{r}
unique_values <- lapply(categorical, unique)
unique_values <- lapply(unique_values, function(x) sort(x) ) # here it excluded NA values out idk why

unique_values
```

**Question 2a: Comparison**

```{r}
colSums(is.na(VC %>% filter(Country == focus_country)))
#This means we cant do this directly to our focus country.
```

```{r}
numerical <- lapply(numerical, function(x) {
  ifelse(is.na(x), ceiling(mean(x, na.rm = TRUE)), x)
})
```

colSums(is.na(numerical))

```{r}
# Impute missing values in numerical columns with ceiling of the mean
numerical <- data.frame(lapply(numerical, function(x) {
  ifelse(is.na(x), ceiling(mean(x, na.rm = TRUE)), x)
}))

# Check the sum of NAs in numerical columns after imputation
colSums(is.na(numerical))
```

```{r}
# Replace the imputed numerical values back into the original VC dataset
VC[numerical_names] <- numerical

# Check if there are any remaining NA values in the entire dataset
colSums(is.na(VC))
```

```{r}
VC <- VC %>% filter(complete.cases(select(., all_of(names(VC)))))
```

Defining 2 dataframes (containing/ excluding)

```{r}
# FIrst we separate the VC data into one with focus country and the other one with other country,

VC_focus <- VC %>% filter(Country == focus_country)
VC_other <- VC %>% filter(Country != focus_country)
```

```{r}
# Then we define a function that separate each VC data into categorical and numerical.

process_data <- function(df) {
  list(
    numerical = df %>% select(-all_of(intersect(categorical_names, names(VC)))),
    categorical = df %>% select(-all_of(intersect(categorical_names, names(VC))))
  )
}

focus_data <- process_data(VC_focus)
other_data <- process_data(VC_other)

# We call out VC_focus/ VC_other when all the whole data needed
# We would call out focus_data/ other_data when categorical/ numerical data need to be treated separately.
# i.e: when categorical data of focus country is needed, it is called by calling out focus_data$categorical
```

Difference in data format

```{r}
dim(VC_focus)
dim(VC_other)
```

Visualisation of all numerical values

```{r}
# To avoid messy, we pre-define a function that create comparative boxplot
compare_numerical <- function(focus_num, other_num, title_suffix = "") {
  
  # Combine data for plotting
  plot_data <- bind_rows(
    focus_num %>% mutate(Group = "Focus"),
    other_num %>% mutate(Group = "Other")
  ) %>% 
    pivot_longer(-Group, names_to = "Variable", values_to = "Value") %>% 
    drop_na(Value)  # Remove missing values
  
  # Create plot
  ggplot(plot_data, aes(x = Value, y = Variable, fill = Group)) +
    geom_boxplot(position = position_dodge(0.8), alpha = 0.7) +
    labs(title = paste("Numerical Variables Comparison", title_suffix),
         x = "Value", y = "")+
    
  theme_minimal()
}
```

```{r}

# pre-define separation of variables
split_point <- ceiling(length(numerical_names) / 3)
first_part_vars <- numerical_names[1:split_point]
second_part_vars <- numerical_names[(split_point+1):(2*(split_point))]
second_part_vars <- setdiff(second_part_vars, c("Age"))
third_part_vars <- numerical_names[(2*(split_point)+1):length(numerical_names)]
```

```{r}
# Create comparisons
comparisons <- list()

# Compare first part
comparisons$first_part <- compare_numerical(
  focus_num = VC_focus %>% select(all_of(first_part_vars)),
  other_num = VC_other %>% select(all_of(first_part_vars)),
  title_suffix = "(First Part)"
)

# Compare second part
comparisons$second_part <- compare_numerical(
  focus_num = VC_focus %>% select(all_of(second_part_vars)),
  other_num = VC_other %>% select(all_of(second_part_vars)),
  title_suffix = "(Second Part)"
)

# Compare Age separately 
comparisons$age <- compare_numerical(
  focus_num = VC_focus %>% select(Age),
  other_num = VC_other %>% select(Age),
  title_suffix = "(Age)"
)

# Compare third part
comparisons$third_part <- compare_numerical(
  focus_num = VC_focus %>% select(all_of(third_part_vars)),
  other_num = VC_other %>% select(all_of(third_part_vars)),
  title_suffix = "(Third Part)"
)

# Display plots
comparisons
```

```{r}
comparisons$age
```

Correlation Matrix

```{r}
cor_plot <- function(data, plot_title) {
   cor_matrix <- data %>% 
  select(where(is.numeric)) %>%  
   cor(use = "complete.obs")      
  
  melted_cor <- melt(cor_matrix, na.rm = TRUE)
  
  ggplot(melted_cor, aes(Var1, Var2, fill = value)) +
    geom_tile(color = "white") +  # Add tile layer for the heatmap
    scale_fill_gradient2(low = "blue", mid = "white", high = "red",
                        midpoint = 0, limit = c(-1,1), name = "Correlation") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          axis.title = element_blank(),
          panel.grid = element_blank(),
          plot.title = element_text(hjust = 0.5)) +  # Center the title
    coord_fixed() +
    labs(title = plot_title)
}
```

```{r}
focus_plot <- cor_plot(focus_data$numerical, paste("Correlation Matrix -", focus_country))
other_plot <- cor_plot(other_data$numerical, "Correlation Matrix - Other Countries")

focus_plot
other_plot
```

**Question 2b, 2c & 3b: Finding significant and most important predictor**

```{r}
# very obviously the following are predefined variables of social organisation conficence
confidence_cols <- c("CReligious", "CArmedForces", "CPress", "CTelevision", "CUnions", "CPolice", "CCourts", "CGovernment", "CPParties", "CParliament", "CCivilService", "CUniversities", "CElections", "CMajCompanies", "CBanks", "CEnvOrg")
```

```{r}
focus_data$confidence <- focus_data$numerical[, names(focus_data$numerical) %in% confidence_cols]
focus_data$predictors <- focus_data$numerical[, !names(focus_data$numerical) %in% confidence_cols]

other_data$confidence <- other_data$numerical[, names(other_data$numerical) %in% confidence_cols]
other_data$predictors <- other_data$numerical[, !names(other_data$numerical) %in% confidence_cols]
```

```{r}
rsquared <- function(confidence, predictors) {

  model_data <- data.frame(confidence, predictors)
  
  # Fit linear model
  model <- lm(confidence ~ ., data = model_data)
  
  # Return R-squared
  summary(model)$r.squared
}
```

```{r}
p_value <- function(confidence, predictors) {
  model_data <- data.frame(confidence = confidence, predictors)
  model <- lm(confidence ~ ., data = model_data)
  
  coef_summary <- summary(model)$coefficients
  predictor_names <- rownames(coef_summary)[-1]  # Remove intercept since we don wan
  
  # Return data frame of results
  result <- data.frame(
    Coefficient = coef_summary[predictor_names, "Estimate"],
    P_value = coef_summary[predictor_names, "Pr(>|t|)"],
    stringsAsFactors = FALSE
  )
  result <- result %>% filter(P_value < 0.05)

  return(result)
}
```

```{r}
analyse_confidence <- function(data) {
  
  # Initialise results list
  results_list <- list()
  
  # Analyse each confidence measure
  for (i in 1:ncol(data$confidence)) {
    conf_name <- colnames(data$confidence)[i]
    res <- p_value(data$confidence[, i], data$predictors)
    res$Confidence <- conf_name
    results_list[[i]] <- res
  }
  
  return(results_list)
}
```

```{r}
plot_predictor_frequency <- function(results_list) {
  
  all_predictors <- unlist(lapply(results_list, function(x) rownames(x)))
  
    predictor_counts <- as.data.frame(table(all_predictors))
  names(predictor_counts) <- c("Predictor", "Freq")
  
   predictor_counts <- predictor_counts[order(-predictor_counts$Freq), ]
  
    predictor_counts <- predictor_counts[predictor_counts$Predictor != "", ]
  
  # Create plot
  ggplot(predictor_counts, aes(x = reorder(Predictor, Freq), y = Freq)) +
    geom_bar(stat = "identity", fill = "#1E90FF") +
    geom_text(aes(label = Freq), hjust = -0.2, size = 3.5) +
    coord_flip() +
    labs(title = "Frequency of Significant Predictors Across Models",
         x = "Predictor Variable",
         y = "Number of Models") +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
      plot.subtitle = element_text(hjust = 0.5, size = 10),
      axis.text.y = element_text(size = 11),
      panel.grid.major.y = element_blank()
    ) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.1))) # Add space for labels
}
```

```{r}
summarise_predictors <- function (results_list){

  conf <- character()
  nrow <- numeric()
  
  for (result in results_list) {
    conf <- c(conf, unique(result$Confidence))  
    nrow <- c(nrow, nrow(result))              
  }
  
  # Create the final data frame
  predictor_counts <- data.frame(
    Confidence = conf,
    Number_of_predictors = nrow
  )
  
  return (predictor_counts)
}
```

**Question 2b**

```{r}
focus_rsquared_results <- sapply(focus_data$confidence, rsquared, 
                          predictors = focus_data$predictors)

focus_rsquared_results
```

```{r}
focus_results <- analyse_confidence(focus_data)
focus_results
```

```{r}
plot_predictor_frequency(focus_results)
```

```{r}
summarise_predictors(focus_results)
```

**Question 2c**

```{r}
other_rsquared_results <- sapply(other_data$confidence, rsquared, 
                          predictors = other_data$predictors)

other_rsquared_results
```

```{r}
other_results <- analyse_confidence(other_data)
other_results
```

```{r}
plot_predictor_frequency(other_results)
```

```{r}
summarise_predictors(other_results)
```

**Question 3a: Clustering**

```{r}
ghs = read.csv("GHX_INDEX_202204.csv")

# The following are all countries available in VC data too. 
selected_countries <- c("Andorra", "Argentina", "Armenia", "Australia", "Bangladesh", "Bolivia", "Brazil", "Canada", "Chile", "China", "Colombia", "Cyprus", "Czech Republic", "Germany", "Ecuador", "Egypt", "Ethiopia", "Great Britain", "Greece", "Guatemala", "Hong Kong", "Indonesia", "India", "Iran", "Iraq", "Jordan", "Japan", "Kazakhstan", "Kenya", "Kyrgyzstan", "South Korea", "Lebanon", "Libya", "Macedonia", "Morocco", "Moldova", "Mexico", "Myanmar", "Mongolia", "Malaysia", "Nigeria", "Nicaragua", "Netherlands", "New Zealand", "Pakistan", "Peru", "Philippines", "Puerto Rico", "Romania", "Russia", "Singapore", "Serbia", "Slovakia", "Thailand", "Tajikistan", "Tunisia", "Turkey", "Taiwan", "Ukraine", "Uruguay", "United States", "Uzbekistan", "Venezuela", "Viet Nam", "Zimbabwe")
```

```{r}
dim(ghs)
```

```{r}
ghs_clean <- ghs %>%
  
  filter(Country %in% selected_countries) %>%
  
  drop_na() %>%
  
  filter(if_all(where(is.numeric), ~ abs(as.vector(scale(.))) <= 3))
```

```{r}
sapply(ghs,class)
```

```{r}
summary(ghs)
```

```{r}
ghs_scaled = scale(ghs[,2:length(names(ghs))])
```

```{r}
ncol(ghs)
```

```{r}
set.seed(33521352)
ghskfit <- kmeans(ghs_scaled, centers = 5, nstart = 20)
ghskfit
```

```{r}
library(cluster)

i_silhouette_score <- function(k){
  km <- kmeans(ghs_scaled, centers = k, nstart = 25)
  ss <- silhouette(km$cluster, dist(ghs_scaled)) 
  mean(ss[, 3])  
}

k <- 2:8
avg_sil <- sapply(k, i_silhouette_score)

plot(k, avg_sil, type = 'b', 
     xlab = 'Number of clusters',
     ylab = 'Average Silhouette Scores',
     main = 'Silhouette Analysis') 
```

```{r}
best_ghskfit <- kmeans(ghs_scaled, centers = 2, nstart = 20) 
best_ghskfit
```

```{r}
cluster_country_table <- table(actual = ghs$Country, fitted = best_ghskfit$cluster)
head(cluster_country_table,10)
```

```{r}

# 1. First, find which cluster the focus country belongs to
focus_cluster <- ghskfit$cluster[ghs$Country == focus_country_full]
focus_cluster
#The result means it appeared in each of these clusters.
```

```{r}

# 2. Then find all countries in the same cluster
similar_countries <- ghs$Country[ghskfit$cluster == focus_cluster]


# 3. Then print the results
similar_countries_data <- ghs[ghs$Country %in% similar_countries & ghs$Country != "Andorra", ]

similar_countries_data
```

**Question 3b**

```{r}
head(similar_countries_data$Country, 5)
```

```{r}
VC_cluster <- VC %>% 
  filter(Country %in% c("BGD", "BOL", "EGY",  "IRN"))
cluster_data <- process_data(VC_cluster)
```

```{r}
cluster_data$confidence <- cluster_data$numerical[, names(cluster_data$numerical) %in% confidence_cols]
cluster_data$predictors <- cluster_data$numerical[, !names(cluster_data$numerical) %in% confidence_cols]
```

```{r}
cluster_rsquared_results <- sapply(cluster_data$confidence, rsquared, 
                          predictors = cluster_data$predictors)

cluster_rsquared_results
```

```{r}
cluster_results <- analyse_confidence(cluster_data)
cluster_results
```

```{r}
summarise_predictors(cluster_results)
```

*END OF APPENDIX*

------------------------------------------------------------------------
